A standard for the scholarly citation of archaeological data as an incentive to data sharing

### 2017-12-29 analysis/paper/paper.Rmd
working on reference list

Sharing of data is a quality that is fundamental to the definition of science (cf. Merton’s (1942) communalism norm, where intellectual property rights are normally given up in exchange for recognition and esteem) and to data both as an abstract quality (cf. the definitions in Table \@ref(tab:summary-of-defs-of-data) that mention data as ‘portable’, ‘stable across different domains’) and as a concrete detail to be managed with policy. For example, for over a decade the National Science Foundation (2016) has had a data sharing policy that states "Investigators are expected to share with other researchers, at no more than incremental cost and within a reasonable time, the primary data, samples, physical collections and other supporting materials created or gathered in the course of work under NSF grants. Grantees are expected to encourage and facilitate such sharing." Surveys of researchers across different domains repeatedly show that people value the ideal of data sharing (Kratz and Strasser 2015). However, data sharing is not widespread in many disciplines, raising questions about why researchers do or do not share their data. Three recent studies have attempted to answer these questions, in the search for strategies to encourage sharing.

@@

@@

Leonelli, S. 
2016.	The Philosophy of Data, In The Routledge Handbook of Philosophy of Information, edited by L. Floridi. Routledge, New York.
Leonelli, S. 
2015.	 What Counts as Scientific Data? A Relational Framework. Philosophy of Science, 82(5), 810-821.
Marwick, B. 
2017.	Computational Reproducibility in Archaeological Research: Basic Principles and a Case Study of their Implementation. Journal of Archaeological Method and Theory, 24(2), 424-450.
Marwick, B., E. Hayes, C. Clarkson and R. Fullagar
2017.	Movement of Lithics by Trampling: An Experiment in the Madjedbebe Sediments, Northern Australia. Journal of Archaeological Science 79:73-85.
McCoy, M. D. and M. C. Codlin
2016.	The Influence of Religious Authority in Everyday Life: A Landscape-Scale Study of Domestic Architecture and Religious Law in Ancient Hawai’i. World Archaeology 48 (3):411–30.
McCullough B. D., K.A. McGeary and T. D. Harrison 
2006.	Lessons from the JMCB Archive. Journal of Money, Credit, and Banking 38(4), 1093-1107.
McCullough B. D. and H. D. Vinod
2005.	Comment: Econometrics and Software. Journal of Economic Perspectives 17(1), 223-224.
McMurry, J. A., Juty, N., Blomberg, N., Burdett, T., Conlin, T., Conte, N., Parkinson, H., Winfree, L., Mungall, C., Haendel, M. and H. Parkinson 
2017.	Identifiers for the 21st Century: How to Design, Provision, and Reuse Persistent Identifiers to Maximize Utility and Impact of Life Science Data. PLOS Biology, 15(6), e2001414. DOI:10.1371/journal.pbio.2001414, accessed on 7 September 2017.
Merton, R.K. 
1942.	The Normative Structure of Science. In The Sociology of Science: Theoretical and Empirical Investigations, edited by R. K. Merton, University Of Chicago Press, Chicago, Illinois. 
Moore, R., and J. Richards
2015.	Here Today, Gone Tomorrow: Open Access, Open Data and Digital Preservation. In Open Source Archaeology: Ethics and Practice, edited by Andrew T. Wilson, Ben Edwards, De Gruyter, Netherlands
Mounce, R. 
2014.	Open Data and Palaeontology. In Issues in Open Research Data, edited by S. A. Moore. pp. 151–164. Ubiquity Press, London.
National Science Foundation
2016.	Dissemination and Sharing of Research Results. Electronic document, https://www.nsf.gov/bfa/dias/policy/dmp.jsp, accessed 7 September 2017
Nicholas, G. P.
2014.	Indigenous cultural heritage in the age of technological reproducibility: Towards a postcolonial ethic of the public domain. In Dynamic Fair Dealing: Creating Canadian Culture Online, edited by Coombe, R. J., Wershler, D., and M. Zeilinger, pp. 213-24. University of Toronto Press, Toronto. 
Nicholas, G. P., and A. Wylie
2012.	Do Not Do Unto Others…’: Cultural misrecognition and the harms of appropriation in an open-source world. In Appropriating the Past: Philosophical Perspectives on Archaeological Practice, edited by R. Coningham and G. Scarre, pp. 195-221, Cambridge University Press, Cambridge.
Nicholas, G. P. and A. Wylie
2009.	Archaeological Finds: Legacies of Appropriation, Modes of Response. The Ethics of Cultural Appropriation, edited by J. O. Young and C. G. Brunk, pp. 11-54, Wiley-Blackwell, Oxford.
Nosek, B. A., Alter, G., Banks, G. C., Borsboom, D., Bowman, S. D., Breckler, S. J. and T.  Yarkoni
2015.	Promoting an Open Research Culture: Author Guidelines for Journals Could Help to Promote Transparency, Openness, and Reproducibility. Science, 348, 1422–5.
Nugent, R., & Williams, H. 
2012.	Sighted surfaces: ocular agency in early Anglo-Saxon cremation burials. In Encountering Imagery: Materialities, Perceptions, Relations, edited by I.-M. Back Danielsson, F. Fahlander and Y. Sjöstrand. pp. 187-208, Stockholm University, Stockholm.
Nuijten, M. B., Borghuis, J., Veldkamp, C. L. S., Alvarez, L. D., van Assen, M. A. L. M., and J. M. Wicherts
2017.	Journal Data Sharing Policies and Statistical Reporting Inconsistencies in Psychology. Electronic document, https://psyarxiv.com/sgbta, accessed 7 September 2017
National Science Foundation
2010.	Data Management & Sharing Frequently Asked Questions (FAQs). Electronic document, https://www.nsf.gov/bfa/dias/policy/dmpfaqs.jsp#1, accessed on 7 September 2017
Pampel, H., Vierkant, P., Scholze, F., Bertelmann, R., Kindling, M., Klump, J. and U. Dierolf
2013	Making research data repositories visible: The re3data.org registry. PloS ONE, 8(11), e78080, DOI: 10.1371/journal.pone.0078080, accessed 7 September 2017.
Pavlech, L. L.
2016	 Data Citation Index. Journal of the Medical Library Association, 104(1), 88–90.
Peng R. D., F. Dominici F, and S. L. Zege
2006.	 Reproducible Epidemiological Research. American Journal of Epidemology 163, 783-789
Penev L, Mietchen D, Chavan V, Hagedorn G, Smith V, Shotton D, Ó Tuama É, Senderov V, Georgiev T, Stoev P, Groom Q, Remsen D, and S. Edmunds
2017	Strategies and guidelines for Scholarly Publishing of Biodiversity Data. Research Ideas and Outcomes 3: e12431. DOI:10.3897/rio.3.e12431, accessed 7 September 2017.
Pienta, A. M., Alter, G. C., and J. A Lyle
2010	The Enduring Value of Social Science Research: The Use and Reuse of Primary Research Data. Electronic document, http://deepblue.lib.umich.edu/handle/2027.42/78307, accessed 27 September 2017
Piwowar H. A., R. S. Day and D. B. Fridsma 
2007.	Sharing Detailed Research Data is Associated with Increased Citation Rate. PLOS ONE 2(3): e308. 
Piwowar, H. A. and T. J. Vision
2013.	Data reuse and the open data citation advantage. PeerJ, 1, e175. DOI:10.7717/peerj.175 accessed on 7 September 2017
PLoS Medicine Editorial and Publishing Policies. 
2017.	Sharing of Materials, Methods and Data. PLoS Medicine Editorial and Publishing Policies. Electronic document. http://journals.plos.org/plosmedicine/policies.php#sharing, accessed on 7 September 2017
Reichman, J. H., and P. F. Uhlir
2003.	A Contractually Reconstructed Research Commons for Scientific Data in a Highly Protectionist Intellectual Property Environment. Law and Contemporary Problems, 66(1/2), 315-462.
Reidpath D. D. and P. A. Allotey
2002.	Data Sharing in Medical Research: An Empirical Investigation. Bioethics 15(2), 125- 134.
Rowhani-Farid, A., Allen, M., and A. G.Barnett
2017.	What Incentives Increase Data Sharing in Health and Medical Research? A Systematic Review. Research Integrity and Peer Review, 2(1), 4. 
Savage C. J. and A. J. Vickers
2009.	Empirical Study of Data Sharing by Authors Publishing in PLoS Journals. PLoS ONE 4(9): e7078. doi:10.1371/journal.pone.0007078, accessed 7 September 2017.
Sawyer, S. 
2008.	Data Wealth, Data Poverty, Science and Cyberinfrastructure. Prometheus, 26(4), 355-371.
Scientific Data Editors
n.d	 Recommended Data Repositories. Electronic document, https://www.nature.com/sdata/policies/repositories, accessed 13 September 2017
Sears, J.R.L 
2011.	Data Sharing Effect on Article Citation Rate in Paleoceanography. Presented at Fall Meeting of the American Geophysical Union. Electronic document, https://doi.org/10.6084/M9.FIGSHARE.1222998.V1, accessed 7 September 2017.
Spencer, H.
2010.	Thoughts on the Sharing of Data and Research Materials and the Role of Journal Policies. Electronic document, https://web.stanford.edu/~vcs/Nov21/hilary_spencer_rdcscsJan2010.pdf, accessed 7 September  2017
Strasser, C., Cook, R., Michener, W. and A. Budden
2012.	Primer on Data Management: What you always wanted to know. DataONE Best Practices Primer. Electronic document, https://doi.org/10.5060/D2251G48, accessed, 7 September 2017 
Stodden, V. 
2010.	The Scientific Method in Practice: Reproducibility in the Computational Sciences, Columbia University Academic Commons, Electronic document, http://hdl.handle.net/10022/AC:P:11417, Accessed 7 September 2017.
Stodden, V. 
2009a.	The Legal Framework for Reproducible Scientific Research: Licensing and Copyright. Computing in Science & Engineering, 11(1), 35-40.
Stodden, V.
2009b.	Enabling Reproducible Research: Open Licensing for Scientific Innovation. International Journal of Communications Law and Policy. https://ssrn.com/abstract=1362040, accessed 7 September 2017.
Tenopir, C., Dalton, E. D., Allard, S., Frame, M., Pjesivac, I., Birch, B and K. Dorsett
2015.	Changes in Data Sharing and Data Reuse Practices and Perceptions among Scientists Worldwide. PLOS ONE, 10(8), e0134826. DOI:10.1371/journal.pone.0134826, accessed 7 September 2017.
Thessen, A. E. and D. J. Patterson 
2011.	Data issues in the life sciences. ZooKeys 150, 15–51. DOI:10.3897/zookeys.150.1766, accessed 7 September 2017. 
Tsosie, R. 
2007. Cultural Challenges to Biotechnology: Native American Genetic Resources and the Concept of Cultural Harm. The Journal of Law, Medicine & Ethics 35(3), 396–411. 
Uhlir, P.F., & Cohen, D. 
2011. Internal document. Board on Research Data and Information, Policy and Global Affairs Division, National Academy of Sciences. 18 March 2011. Washington, DC.
Archaeology Data Service / Digital Antiquity 
2011. Guides to Good Practice. Electronic document, http://guides.archaeologydataservice.ac.uk/ accessed on 7 September 2017. 
Vanpaemel, W., Vermorgen, M., Deriemaecker, L., and G. Storms
2015. 	Are We Wasting a Good Crisis? The Availability of Psychological Research Data after the Storm. Collabra, 1(1): 3. DOI:10.1525/collabra.13, accessed 7 September 2017. 
Vines, T.H, A. Y. Albert, R. L. Andrew, F. Débarre, D. G.Bock, M. T. Franklin and D. J.  Rennison
2014.	 The Availability of Research Data Declines Rapidly with Article Age. Current Biology 24(1):94-97.
Vitelli, K. D. and J. S. Colwell-Chanthaphonh, (editors)
2006.	Archaeological Ethics. Rowman Altamira, New York.
Wallis, J. C., Rolando, E. and C. L. Borgman
2013.	If We Share Data, Will Anyone Use Them? Data Sharing and Reuse in the Long Tail of Science and Technology. PLoS ONE, 8(7), e67332. DOI:10.1371/journal.pone.0067332, accessed 7 September 2017.
White E, Baldridge E, Brym Z, Locey K, McGlinn D and S. Supp
2013.	 Nine simple ways to make it easier to (re)use your data. Ideas in Ecology and Evolution. 2013;6: 1–10. DOI:10.4033/iee.2013.6b.6.f, accessed on 7 September 2017
Whitlock, M. C. 
2011.	Data Archiving in Ecology and Evolution: Best Practices. Trends in Ecology & Evolution, 26(2), 61-65.
Wicherts, J. M., Borsboom, D., Kats, J. and D. Molenaar
2006.	The Poor Availability of Psychological Research Data for Reanalysis. American Psychologist, 61(7), 726.
Wilkinson, M. D., Dumontier, M., Aalbersberg, I. J., Appleton, G., Axton, M., Baak, A. and P. E. Bourne
2016.	The FAIR Guiding Principles for scientific data management and stewardship. Scientific Data, 3, 160018. DOI:10.1038/sdata.2016.18, accessed on 7 September 2017.
Womack R.P.
2015.	Research Data in Core Journals in Biology, Chemistry, Mathematics, and Physics. PLOS ONE 10(12): e0143460. DOI:10.1371/journal.pone.0143460, accessed on 7 September 2017. 
Wouters P. and W. Haak 
2017.	Open Data Report: The Researcher Perspective. Electronic document https://www.elsevier.com/about/open-science/research-data/open-data-report, accessed 11 October 2017
Zimmerman, L. J., Vitelli, K. D., and J. Hollowell-Zimmer, (editors)
2003.	Ethical Issues in Archaeology. Rowman Altamira, New York.

>>>>

Sharing of data is a quality that is fundamental to the definition of science (cf. Merton’s (1942) communalism norm, where intellectual property rights are normally given up in exchange for recognition and esteem) and to data both as an abstract quality (cf. the definitions in Table \@ref(tab:summary-of-defs-of-data) that mention data as ‘portable’, ‘stable across different domains’) and as a concrete detail to be managed with policy. For example, for over a decade the National Science Foundation (2016) has had a data sharing policy that states "Investigators are expected to share with other researchers, at no more than incremental cost and within a reasonable time, the primary data, samples, physical collections and other supporting materials created or gathered in the course of work under NSF grants. Grantees are expected to encourage and facilitate such sharing." Surveys of researchers across different domains repeatedly show that people value the ideal of data sharing (Kratz and Strasser 2014; 2015). However, data sharing is not widespread in many disciplines, raising questions about why researchers do or do not share their data. Three recent studies have attempted to answer these questions, in the search for strategies to encourage sharing.

@@

Archaeology Data Service / Digital Antiquity 
2011  Guides to Good Practice. Electronic document, http://guides.archaeologydataservice.ac.uk/ accessed on 7 September 2017.

@@

Leonelli, Sabina 
2015	 What Counts as Scientific Data? A Relational Framework. _Philosophy of Science_ 82(5): 810-821.

Leonelli, Sabina 
2016	The Philosophy of Data, In _The Routledge Handbook of Philosophy of Information_, edited by L. Floridi. Routledge, New York.

Marwick, Ben 
2017	Computational Reproducibility in Archaeological Research: Basic Principles and a Case Study of their Implementation. _Journal of Archaeological Method and Theory_ 24(2): 424-450.

Marwick, Ben, Elspeth Hayes, Chris Clarkson and Richard. Fullagar
2017	Movement of Lithics by Trampling: An Experiment in the Madjedbebe Sediments, Northern Australia. _Journal of Archaeological Science_ 79:73-85.

McCoy, Mark D. and Maria C. Codlin
2016	The Influence of Religious Authority in Everyday Life: A Landscape-Scale Study of Domestic Architecture and Religious Law in Ancient Hawai’i. _World Archaeology_ 48(3):411–30.

McCullough, Bruce D., Kerry A. McGeary and Teresa D. Harrison 
2006	Lessons from the JMCB Archive. _Journal of Money, Credit, and Banking_ 38(4): 1093-1107.

McCullough Bruce D. and Hrishikesh D. Vinod
2005	Comment: Econometrics and Software. _Journal of Economic Perspectives_ 17(1): 223-224.

McMurry, Julie A., Nick Juty, Niklas Blomberg, Tony Burdett, Tom Conlin, Nathalie Conte and Helen Parkinson 
2017	Identifiers for the 21st Century: How to Design, Provision, and Reuse Persistent Identifiers to Maximize Utility and Impact of Life Science Data. _PLOS Biology_ 15(6), e2001414. DOI:10.1371/journal.pbio.2001414, accessed on 7 September 2017.

Merton, Robert K. 
1942	The Normative Structure of Science. In _The Sociology of Science: Theoretical and Empirical Investigations_, edited by Robert K. Merton, University Of Chicago Press, Chicago, Illinois.

Moore, Ray, and Julian Richards
2015	Here Today, Gone Tomorrow: Open Access, Open Data and Digital Preservation. In _Open Source Archaeology: Ethics and Practice_, edited by Andrew T. Wilson, Ben Edwards, De Gruyter, Netherlands

Mounce, Ross. 
2014	Open Data and Palaeontology. In _Issues in Open Research Data_, edited by S. A. Moore. pp. 151–164. Ubiquity Press, London.

National Science Foundation
2016	Dissemination and Sharing of Research Results. Electronic document, https://www.nsf.gov/bfa/dias/policy/dmp.jsp, accessed 7 September 2017

Nicholas, George P.
2014	Indigenous cultural heritage in the age of technological reproducibility: Towards a postcolonial ethic of the public domain. In _Dynamic Fair Dealing: Creating Canadian Culture Online_, edited by Rosemary Coombe, Darren Wershler and Martin Zeilinger, pp. 213-24. University of Toronto Press, Toronto.

Nicholas, George P. and Alison Wylie
2009	Archaeological Finds: Legacies of Appropriation, Modes of Response. In _The Ethics of Cultural Appropriation_, edited by James O. Young and Conrad G. Brunk, pp. 11-54, Wiley-Blackwell, Oxford.

Nicholas, George P. and Alison Wylie
2012	Do Not Do Unto Others…’: Cultural misrecognition and the harms of appropriation in an open-source world. In _Appropriating the Past: Philosophical Perspectives on Archaeological Practice_, edited by Robin Coningham and Geoffrey Scarre, pp. 195-221, Cambridge University Press, Cambridge.

Nosek, B. A., Alter, G., Banks, G. C., Borsboom, D., Bowman, S. D., Breckler, S. J. and T.  Yarkoni
2015	Promoting an Open Research Culture: Author Guidelines for Journals Could Help to Promote Transparency, Openness, and Reproducibility. _Science_ 348: 1422–5.

Nugent, Ruth & Howard Williams 
2012	Sighted surfaces: ocular agency in early Anglo-Saxon cremation burials. In _Encountering Imagery: Materialities, Perceptions, Relations_, edited by Ing-Marie Back Danielsson, Fredrik Fahlander and Ylva Sjöstrand. pp. 187-208, Stockholm University, Stockholm.

Nuijten, Michèle B., Jeroen Borghuis, Coosje Veldkamp, Linda Alvarez, Marvel van Assen and Jelte M. Wicherts
2017	Journal Data Sharing Policies and Statistical Reporting Inconsistencies in Psychology. _Collabra: Psychology_ 3(1), 31. DOI:10.1525/collabra.102, accessed 7 September 2017.

National Science Foundation
2010	Data Management & Sharing Frequently Asked Questions (FAQs). Electronic document, https://www.nsf.gov/bfa/dias/policy/dmpfaqs.jsp#1, accessed on 7 September 2017

Pampel, Heinz, Paul Vierkant, Frank Scholze, Roland Bertelmann, Maxi Kindling, Jens Klump and Uwe Dierolf
2013	Making research data repositories visible: The re3data.org registry. _PloS ONE_ 8(11), e78080, DOI:10.1371/journal.pone.0078080, accessed 7 September 2017.

Pavlech, Laura L.
2016	 Data Citation Index. _Journal of the Medical Library Association_ 104(1): 88–90.

Peng Roger D., Francesca Dominici  and Scott L. Zege
2006	 Reproducible Epidemiological Research. _American Journal of Epidemology_ 163: 783-789.

Penev, Lyubomir, Daniel Mietchen, Vishwas Shravan Chavan, Gregor Hagedorn, Vincent Stuart Smith, David Shotton, Éamonn Ó Tuama, Viktor Senderov, Teodor Georgiev, Pavel Stoev, Quentin John Groom, David Remsen and Scott C. Edmunds
2017	Strategies and guidelines for Scholarly Publishing of Biodiversity Data. _Research Ideas and Outcomes_ 3, e12431. DOI:10.3897/rio.3.e12431, accessed 7 September 2017.

Pienta, Amy M., George Alter and Jared A. Lyle
2010	The Enduring Value of Social Science Research: The Use and Reuse of Primary Research Data. Electronic document, http://deepblue.lib.umich.edu/handle/2027.42/78307, accessed 27 September 2017

Piwowar, Heather A., Roger S. Day and Douglas B. Fridsma 
2007	Sharing Detailed Research Data is Associated with Increased Citation Rate. _PLOS ONE_ 2(3): e308.

Piwowar, Heather A. and Todd. J. Vision
2013	Data reuse and the open data citation advantage. _PeerJ_, 1, e175. DOI:10.7717/peerj.175 accessed on 7 September 2017

PLoS Medicine Editorial and Publishing Policies. 
2017	Sharing of Materials, Methods and Data. PLoS Medicine Editorial and Publishing Policies. Electronic document. http://journals.plos.org/plosmedicine/policies.php#sharing, accessed on 7 September 2017

Reichman, James H., and Paul F. Uhlir
2003	A Contractually Reconstructed Research Commons for Scientific Data in a Highly Protectionist Intellectual Property Environment. _Law and Contemporary Problems_ 66(1/2): 315-462.

Reidpath, Daniel D. and Pascale A. Allotey
2002	Data Sharing in Medical Research: An Empirical Investigation. _Bioethics_ 15(2): 125-134.

Rowhani-Farid, Anisa, Michelle Allen and Adrian G. Barnett
2017	What Incentives Increase Data Sharing in Health and Medical Research? A Systematic Review. _Research Integrity and Peer Review_ 2(1): 4. DOI:10.1186/s41073-017-0028-9, accessed 7 September 2017.

Savage Caroline J. and Andrew J. Vickers
2009	Empirical Study of Data Sharing by Authors Publishing in PLoS Journals. _PLoS ONE_ 4(9): e7078. doi:10.1371/journal.pone.0007078, accessed 7 September 2017.

Sawyer, Steve 
2008	Data Wealth, Data Poverty, Science and Cyberinfrastructure. _Prometheus_ 26(4), 355-371.

Scientific Data Editors
n.d	 Recommended Data Repositories. Electronic document, https://www.nature.com/sdata/policies/repositories, accessed 13 September 2017

Sears, Jonathan R. L. 
2011	Data Sharing Effect on Article Citation Rate in Paleoceanography. Presented at Fall Meeting of the American Geophysical Union. Electronic document, https://doi.org/10.6084/M9.FIGSHARE.1222998.V1, accessed 7 September 2017.

Spencer, Hilary.
2010	Thoughts on the Sharing of Data and Research Materials and the Role of Journal Policies. Electronic document, https://web.stanford.edu/~vcs/Nov21/hilary_spencer_rdcscsJan2010.pdf, accessed 7 September2017

Strasser, Carly, Robert Cook, William Michener and Amber Budden
2012	Primer on Data Management: What you always wanted to know. DataONE Best Practices Primer. Electronic document, https://doi.org/10.5060/D2251G48, accessed, 7 September 2017

Stodden, Victoria 
2009a	The Legal Framework for Reproducible Scientific Research: Licensing and Copyright. _Computing in Science & Engineering_ 11(1): 35-40.

Stodden, Victoria
2009b	Enabling Reproducible Research: Open Licensing for Scientific Innovation. _International Journal of Communications Law and Policy_ https://ssrn.com/abstract=1362040, accessed 7 September 2017.

Stodden, Victoria 
2010	The Scientific Method in Practice: Reproducibility in the Computational Sciences, Columbia University Academic Commons, Electronic document, http://hdl.handle.net/10022/AC:P:11417, Accessed 7 September 2017.

Tenopir, Carol, Elizabeth Dalton, Suzie Allard, Mike Frame, Ivanka Pjesivac, Ben Birch and Kristina Dorsett
2015	Changes in Data Sharing and Data Reuse Practices and Perceptions among Scientists Worldwide. _PLOS ONE_ 10(8), e0134826. DOI:10.1371/journal.pone.0134826, accessed 7 September 2017.

Thessen, Anne E. and David J. Patterson 
2011	Data issues in the life sciences. _ZooKeys_ 150, 15–51. DOI:10.3897/zookeys.150.1766, accessed 7 September 2017.

Tsosie, Rebecca 
2007  Cultural Challenges to Biotechnology: Native American Genetic Resources and the Concept of Cultural Harm. _The Journal of Law, Medicine & Ethics_ 35(3), 396–411.

Uhlir, Paul F. and Daniel Cohen 
2011  Internal document. Board on Research Data and Information, Policy and Global Affairs Division, National Academy of Sciences. 18 March 2011. Washington, DC.

Vanpaemel, Wolf, Maarten Vermorgen, Leen Deriemaecker and Gert Storms
2015 	Are We Wasting a Good Crisis? The Availability of Psychological Research Data after the Storm. _Collabra_ 1(1): 3. DOI:10.1525/collabra.13, accessed 7 September 2017.

Vines, Timothy H., Arianne Y. Albert, Rose L. Andrew, Florence Débarre, Dan G. Bock, Michelle T. Franklin and Diana J.  Rennison
2014	 The Availability of Research Data Declines Rapidly with Article Age. _Current Biology_ 24(1):94-97.

Vitelli, Karen D. and John. S. Colwell-Chanthaphonh, (editors)
2006	_Archaeological Ethics_. Rowman Altamira, New York.

Wallis, Jillian C., Elizabeth Rolando and Christine L. Borgman
2013	If We Share Data, Will Anyone Use Them? Data Sharing and Reuse in the Long Tail of Science and Technology. _PLoS ONE_ 8(7), e67332. DOI:10.1371/journal.pone.0067332, accessed 7 September 2017.

White, Ethan, Elita Baldridge, Zachary T. Brym, Kenneth Locey, Daniel McGlinn, and Sarah Supp
2013	 Nine simple ways to make it easier to (re)use your data. Ideas in Ecology and Evolution. 2013(6): 1–10. DOI:10.4033/iee.2013.6b.6.f, accessed on 7 September 2017

Whitlock, Michael C. 
2011	Data Archiving in Ecology and Evolution: Best Practices. Trends in Ecology & Evolution, 26(2), 61-65.

Wicherts, Jelte M., Denny Borsboom, Judith Kats and Dylan Molenaar
2006	The Poor Availability of Psychological Research Data for Reanalysis. _American Psychologist_ 61(7): 726.

Wilkinson, Mark D., Michel Dumontier, Isbrand J. Aalbersberg, Gabrielle Appleton, Myles Axton, Arie Baak and Barend Mons
2016	The FAIR Guiding Principles for scientific data management and stewardship. _Scientific Data_ 3, 160018. DOI:10.1038/sdata.2016.18, accessed on 7 September 2017.

Womack Ryan P.
2015	Research Data in Core Journals in Biology, Chemistry, Mathematics, and Physics. _PLOS ONE_ 10(12): e0143460. DOI:10.1371/journal.pone.0143460, accessed on 7 September 2017.

Wouters Paul and Wouter. Haak 
2017	Open Data Report: The Researcher Perspective. Electronic document https://www.elsevier.com/about/open-science/research-data/open-data-report, accessed 11 October 2017

Zimmerman, Larry J., Karen Vitelli, and Julie Hollowell-Zimmer (editors)
2003	_Ethical Issues in Archaeology_. Rowman Altamira, New York.
